% ------------------------------------------------------------------------ %
% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../Project.tex
% !TEX spellcheck = en-EN
% ------------------------------------------------------------------------ %
%
% ------------------------------------------------------------------------ %
% 	CHAPTER TITLE
% ------------------------------------------------------------------------ %
%
\chapter{Results}
For execution of the test some rules about the task performance are used.
Starting from the scoring method considered for the task success, the one used is the following:
\begin{itemize}
\item Complete success (without assistance) = 1
\item Partial success, or if assistance given = 0.5
\item Gives up or wrong answer = 0
\end{itemize}
For the determination of unsuccessful tasks, a task is considered unsuccessful if one of the following condition is matched:
\begin{itemize}
\item The user give up on trying to complete the task
\item Three wrong paths, or three attempts from the start
\item The cut-off time (threshold) is elapsed (for this test 4 minutes are chosen as cut-off time)
\end{itemize}
At last, action is considered an error if:
\begin{itemize}
\item The user enter incorrect data into a form field
\item The user makes the wrong choice in a menu or drop-down list
\item The user takes an incorrect sequence of actions
\item The user fails to take a key action
\end{itemize}
The tasks' results show that everyone was able to complete all the tasks in a reasonable time and with zero errors. The only noteworthy data are three:
\begin{itemize}
\item On the first task one person took a long time (2 minutes and 21 seconds), made three errors and noted that a link to the ``Who We Are'' page could be added to the content of the homepage. On average this task took more time than the other ones to everybody and another person did one error.
\item On the third task one person made two errors and it took 48 seconds to complete it (not incredibly higher than average time). Also was noted that ``Contact Us'' landmark could be more noticeable.
\item On the fifth task one person made four errors and it took 2 minutes and 11 seconds to complete (pretty higher than average). It was also suggested that the ``Locations'' landmark could be more noticeable.
\end{itemize}
The data collected by survey confirms the task's result, with a good overall impression of the structure and information architecture, content and navigation. Only one person replied neutral at the statement ``It was easy to find the information I needed''.
%
% ------------------------------------------------------------------------ %
%
% -----------------------------END------------------------------------- %