% ------------------------------------------------------------------------ %
% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../Project.tex
% !TEX spellcheck = en-EN
% ------------------------------------------------------------------------ %
%
% ------------------------------------------------------------------------ %
% 	CHAPTER TITLE
% ------------------------------------------------------------------------ %
%
\chapter{Discussion of results}
This chapter is the recap of the results of the testing and a list of recommended interventions to the site, for its improvement.

\section{Problem report}

\subsection{Quantitative data}
Concerning quantitative data retrieved from the test. The site appear intuitive and user friendly since all tasks are performed in less than one minute, compared to the 4 minutes of the cut-off time (never reached).\\
The test registered 12 error from the users, all contained in the execution of three tasks (first, third and fifth). 4 errors in the the first task mean that ``Who We Are'' page title is not effectively understandable and doesn't explain well the content of the page. 3 errors in the third task are related to the difficulty in finding the ``Contact Us'' landmark since it's in the footer at the end of the page. 5 errors in the last task could be defined by the fact that ``Contact Us'' page contains a map, so user that already had done the task about contacts of the association, could be led to use that page instead of ``Locations''.\\
The task success rate is high even in the tasks that gave more problems (minimum task success rate is 80\%), it means that the site is simple and well structured, event tough some initial disorientation or misunderstandings by the users can occur.

\subsection{Qualitative data}
Using the qualitative data obtained by the comments, observations and questionnaires other results can be computed.\\
From the comments of the users and moderator's observations during the execution of the test, the main problem that came up is with the tracing of the right link for the completion of the task.
From the questionnaires emerged the same problem as in the comments and observations, but some users evaluated coldly also the relevance and utility of the text and the capacity of the site to help the users to find what they were looking for.

\section{Final recommendations}
The final recommendations of these report will be divided in three categories:
\begin{itemize}
\item Priority 1: Mandatory and urgent interventions
\item Priority 2: Needed interventions but not urgent
\item Priority 3: Hopeful interventions
\end{itemize}

\subsection{Priority 1}
With higher priority is recommended to change the position of the ``Contact Us'' landmark to a place in the site that is immediately visible for the users. Another urgent intervention to do is to change the name of the page ``Who We Are'' in something like ``What Is The Association'' or ``History And Values'' to highlight the fact that the page describes the history and the scope of the association.

\subsection{Priority 2}
With priority 2 it is recommended to move the map that is located in ``Contact Us'' into ``Locations'' and to add a link from the page of contacts to the map.

\subsection{Priority 3}
With the less important priority, the intervention recommended is to change the style, the color or thedecoration of the links, in order to make them more visible. 
%
% -----------------------------END------------------------------------- %
