% ------------------------------------------------------------------------ %
% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX root = ../Project.tex
% !TEX spellcheck = en-EN
% ------------------------------------------------------------------------ %
%
% ------------------------------------------------------------------------ %
% 	CHAPTER TITLE
% ------------------------------------------------------------------------ %
%
\chapter{Scenarios}
%
%
\begin{itemize}
\item Sergio is a social educator who works with people with disabilities and, at a training conference, he stumbles upon a flyer reading “The Big Family – Growing Up Together” accompanied by a URL. Curious about it, he takes the flyer and he digits the URL on the navigation bar of his smartphone’s browser. The home page of The Big Family’s website loads and he sees a slideshow reading “Our services”, “Our Team”, “Our Location” and under it a paragraph titled “About Us”. That’s what he was looking for, so he reads it and he acknowledges a brief description of the association’s scope. He touches the paragraph title because he wants to know more, and he is redirected to a page titled “Who We Are” where he reads more about the association. Happy of his discovery, he puts the flyer in his pocket looking forward to giving a better look at the association’s offer once at home.
\item Giovanni Giorgio, who recently moved in Certaldo, is the parent of a disabled child and he’s looking for a structure in which his son Francesco can be welcomed and assisted. After a quick search on the internet he discovers that the nearest center to his house is run by “The Big Family” association for disabled children. Looking it up on Google he finds their website and, after reading the “Who We Are” page, he clicks on the “Locations” landmark, chooses the Certaldo’s location and opens the first service. After reading the description he goes back to the location page, using the links of the locations in which the current service is offered, and checks out the other services until he finds the one fitting his son’s needs. He also quickly checks the operators working in that specific service before clicking on the “Contact Us” landmark on the bottom of the page to obtain the secretary’s number. Now he will call them to enroll his son.
\item Angela’s nephew Filippo often attends some services in the Fidenza’s location of “The Big Family” association and today she’s asked to pick him up. Angela doesn’t know the address of the location, so she looks up on Google the association website and, once in, she clicks on “Locations” landmark, then on Fidenza’s location and finally she obtains the address. Now she takes the car and sets the address on the navigator before leaving.
\end{itemize}%
% -----------------------------END------------------------------------- %
